Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-25 3-Introduction.tex
Updates from Overleaf

TODO
MDE has traditionally adopted a two-level,top-down meta-modelling approach, where meta-models reside in a certain meta-level, and models are created one meta-level below by using types from the metamodel (cite MOF and EMF).

>>>>

Model-driven engineering (MDE) has traditionally adopted a two-level, top-down approach, where meta-models reside in a certain meta-level, and models are created one meta-level below by using types from the metamodel (e.g., EMF - \cite{emf} and MOF - \cite{omg2013mof}).

### 2021-05-25 6-ModelPresentation.tex
Updates from Overleaf

\textit{Code} concept extends \textit{SEArtifact}, and defines a relation \textit{language} to \textit{ProgrammingLanguage} with single cardinality (\textbf{S4}). \textbf{S5} is more ambigous as task type \textit{Coding} defines one or more programming languages but produces code which is expressed in one language only. Semantics is unclear relatively to instantiation policy for artifacts. We assume that a Code artifact must be produced for each programming language defined in a \textit{CodingTaskType}. If \textit{COBOL} is referenced in languages defined for a given Coding instance, then we must instantiate a \textit{Code} instance with \textit{COBOL} language (\textbf{S5} and \textbf{S6}).

@@

>>>>

\textit{Code} concept extends \textit{SEArtifact}, and defines a relation \textit{language} to \textit{ProgrammingLanguage} with single cardinality (\textbf{S4}). \textbf{S5} is more ambigous as task type \textit{Coding} defines one or more programming languages but produces code which is expressed in one language only. Semantics is unclear relatively to instantiation policy for artifacts. We assume that task execution implies that for each used artifact type defined in related task type, at least one artifact

Code artifact must be produced for each programming language defined in a \textit{CodingTaskType}. If \textit{COBOL} is referenced in languages defined for a given Coding instance, then we must instantiate a \textit{Code} instance with \textit{COBOL} language (\textbf{S5} and \textbf{S6}).

@@

\begin{figure*}
 \centering
     \includegraphics[width=1.0 \textwidth]{Figures/ToolingArchitecture.pdf}
     \caption{Tooling architecture}
    \label{fig:ToolingArchitecture}
\end{figure*}

### 2021-05-25 8-Discussion.tex
Updates from Overleaf

\todo[inline]{on pourrait aussi répondre ici aux 3 questions posées
explicitement (copiées dansl'intro pour le moment), a priori non, le chef
trouve que c'est chiant}

>>>>

\todo[inline]{on pourrait aussi répondre ici aux 3 questions posées
explicitement (copiées dans l'intro pour le moment), a priori non, le chef
trouve que c'est chiant}
